### 2017-02-28 thesis/discussion/discussion.tex
tmp commit

There were two main aims for this project: firstly to determine whether there were any obesity specific genetic signatures that could be tranferred across multiple cancer types; and secondly to investigate whether there were any biological pathways dysregulated in the samples that were obese compared to the smaples that were not obese.
These aims were addressed in \cref{cha:obesity_genetic_signatures_and_cancer,cha:obesity_associated_genetic_signature_and_pathway_signatures}, resepectively.
\\

@@

The simulation results also showed that the number of \glspl{deg} identified in these cancer types were greater than one would expect by chance.
However, as observed by the results from the simulation, there were many genes identified by chance alone, which suggested that many of the genes found were false positives.

>>>>

There were two main aims to this project: firstly to determine whether there were any obesity specific genetic signatures that could be tranferred across multiple cancer types; and secondly to investigate whether there were any biological pathways dysregulated in the samples that were obese compared to the smaples that were not obese.
These aims were addressed in \cref{cha:obesity_genetic_signatures_and_cancer,cha:obesity_associated_genetic_signature_and_pathway_signatures}, resepectively.
\\

@@

The simulation results also showed that the number of \glspl{deg} identified in these cancer types were greater than one would expect by chance.
However, as observed by the results from the simulation, there were many genes identified by chance alone, which suggested that majority of the \glspl{deg} found in the eight cancer types were false positives.
This apparently high level of \Glspl{type1} was not only observed in the \gls{icgc} data sets, but also in the Creighton \textit{et al.} data set when gene expression analyses were carried out to generate various obesity associated genetic signatures in \cref{sub:identification_of_obesity_associated_genetic_signatures}.

The fact that there were so many false positives in the \glspl{deg} from the \gls{icgc} data sets indicated that the use of the sample \gls{bmi}/\gls{bmi} status as the variable for gene expression analysis was prone to \Glspl{type1}.
This meant that there were very little evidence of true obesity associated genetic signatures in the data sets that have been explored in this project, or perhaps the sample \gls{bmi}/\gls{bmi} status was not enough to pin point the underlying biological relationship between obesity and cancer.
Even if \gls{bmi} and/or \gls{bmi} status was enough to identify the genes that were truly associated with obesity, it would not be a trivial task to identify the truly obesity associated genes from those that were not.
This raises an important question of whether the sample \gls{bmi}/\gls{bmi} status was enough to uncover the true association between obesity and cancer (adressed in \cref{sec:limitations,sec:future_directions}).

Finally, pathway enrichment analysis was carried out in the \gls{icgc} data sets to investigate whether there were any pathways that significantly associated with obesity (\cref{sec:pathways_enriched_in_icgc_data_sets}).
There were no pathways enriched in any of the \gls{icgc} data sets, nor the combined \gls{icgc} data set.
Even though there was no significantly enriched  pathway in the \gls{icgc} data sets, it was evident from the obesity metagenes from Creighton \textit{et al.} and Fuentes-Mattei \textit{et al.} data sets that these metagenes were associated with the gene expressions.
This suggested that the metagenes were able to identify some sort of genetic pattern in the data, even though these metagenes were not significantly associated with obesity.
\\

\noindent
In \cref{cha:obesity_associated_genetic_signature_and_pathway_signatures}, analyses were carried out to determine what the genetic pattern the obesity metagenes from \cref{cha:obesity_genetic_signatures_and_cancer} were associating with.
